Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-01 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
More framework description

\section{HC  IEC Framework}
  \subsection{Real World}
  \subsection{Data Model}
  \subsection{Evolutionary Algorithm}

>>>>

\section{HC  IEC Framework}
% Comment: 
% Maybe in this case we should use the term software framework or architecture. 
The general goal of this research is to develop a human-centered \cite{gasson2003human} 
software framework for interactive evolutionary computation (IEC). 
The framework is a reusable architectural design together with an implementation \cite{campbell1991choices}, 
providing generalized components to developers of IEC systems. In the description we deliberately use the more general term Human instead of User, because humans are not always playing the role of users in software engineering sense, they could just be interacting naturally with their environment and with out knowing they are implicitly
evaluating a possible solution. The framework includes components that can be refined to increase
participation and also to minimize the amount of evaluations needed for the evolutionary process in a given IEC application.

  \subsection{Real World}
  \subsection{Data Model}
  \subsection{Evolutionary Algorithm}
